Isotope data reduction

### 2019-12-07 isotope_data_reduction.rmd
added new plots and map peaks

```{r}
sample_files_w_ids %>% 
  iso_get_peak_table(include_file_info = everything()) %>% 
  filter(compound != "unknown") %>% 
  mutate(sample_label = iso_format(control, inc_time, with_glu)) %>% 
  iso_plot_data(
    x = compound, y = c(area2, d2H), color = sample_label,
    points = TRUE
  )
```

>>>>

```{r}
real_data <- 
  sample_files_w_ids %>% 
  iso_get_peak_table(include_file_info = everything()) %>% 
  filter(compound != "H2") %>% 
  group_by(file_id) %>% 
  mutate(rel_amount = area2 / sum(area2[compound != "IS"])) %>% 
  ungroup() %>% 
  filter(compound != "unknown") 
```

```{r}
real_data %>% 
  mutate(sample_label = iso_format(control, inc_time, with_glu)) %>% 
  iso_plot_data(
    x = inc_time, y = d2H, color = compound, shape = with_glu, size = rel_amount,
    points = TRUE,
    lines = TRUE,
    panel = with_glu ~ .
    #panel_scales = "fixed"
  )
```

# FOR PROCESSING ONLY

# Export data

```{r}
irms_example_data <- 
  sample_files_w_ids %>%
  iso_filter_files(analysis == 5689) %>% 
  iso_get_peak_table() %>% 
  filter(compound != "H2") %>% 
  select(rt, rt_start, rt_end, amp2, area2) %>% 
  mutate(rel_height = amp2/sum(amp2) * 100) %>% 
  filter(rel_height > 1)

irms_example_data %>% 
  openxlsx::write.xlsx(file.path("tables", "gc_irms_single_sample_peak_table.xlsx"))
```

# Peak Mapping help

```{r}
tsq_example_data <- read_excel(file.path("tables", "tsq_single_sample_peak_table.xlsx"))
```

```{r}
bind_rows(
  irms_example_data %>% mutate(type = "irms") %>% iso_strip_units(),
  tsq_example_data %>% mutate(type = "tsq")
) %>% 
  ggplot() +
  aes(rt, rel_height, label = paste0(`Peak Name`, "\n", round(rt))) +
  geom_bar(stat = "identity")+
  ggrepel::geom_text_repel(color = "red", alpha = 0.5, min.segment.length = 0)+
  facet_grid(type ~ .)
ggsave(file.path("figures", "irms_tsq_comparison.pdf"), width = 12, height = 8)
```

##
```{r}
# examine variation in the reference peaks
sample_files_w_ids %>% 
  # focus on reference peaks only
  filter(!is.na(ref_nr)) %>% 
  # mark ref peak used for raw delta values (assuming the same in all anlysis)
  mutate(
    ref_info = paste0(ref_nr, ifelse(is_ref == 1, "*", "")) %>% factor() %>% fct_inorder()
  ) %>% 
  # visualize
  iso_plot_ref_peaks(
    # specify the ratios to visualize
    x = Analysis, ratio = `r45/44`, fill = ref_info,
    panel_scales = "fixed"
  ) +
  labs(x = "Analysis", fill = "Reference\npeak")
```

##
```{r}
# focus on analyte peaks and calculate useful summary statistics
peak_table_analytes <- sample_files_w_ids %>% 
  # omit reference peaks for further processing (i.e. analyte peaks only)
  filter(is.na(ref_nr)) %>% 
  # for each analysis, calculate a few useful summary statistics
  iso_mutate_peak_table(
    group_by = file_id,
    rel_area = area44 / sum(area44, na.rm = TRUE),
    # calculate mean area for all peaks
    mean_area = mean(area44, na.rm = TRUE),
    # calculate mean area and amplitude for identified peaks
    mean_area_identified = mean(area44[!is.na(compound)], na.rm = TRUE),
    mean_amp_identified = mean(amp44[!is.na(compound)], na.rm = TRUE)
  )
```

##
```{r}
# find files with linearity in the Identifier 1 field
lins <- iso_files %>% iso_filter_files(type == "lin") 
#> Info: applying file filter, keeping 1 of 45 files

# visualize the linearity runs
iso_plot_continuous_flow_data(lins, data = 44, color = format(file_datetime))

```

##
```{r}
# calculate on/off summary
on_off_summary <- 
  on_offs %>% 
  # retrieve peak table
  iso_get_peak_table(
    select = c(amp44, area44, d13C),
    include_file_info = c(file_datetime, id2)
  ) %>% 
  # summarize information
  group_by(file_datetime, id2) %>% 
  iso_summarize_data_table() 
#> Info: aggregating peak table from 4 data file(s), including file info 'c(file_datetime, id2)'

# table
on_off_summary %>% iso_make_units_explicit() %>% knitr::kable(digits = 3)
```
